---
title: "data manipulation hands-on"
author: "YOURNAME"
date: "`r Sys.Date()`"
---

```{r}
library(knitr)
library(tidyverse)
library(PKPDmisc)
```

```{r}
pk_data <- read_csv("../data/pk_data.csv")
```

```{r}
head(pk_data)
```


## DATA MANIPULATION

The goals of this section:

* Use data manipulation tools to prepare the dataset for analysis


1.  Rename "DV" column as "COBS"

```{r}
pk_data_cobs <- pk_data %>% rename(COBS = DV)
```


4. Perform the following tasks:

a. Ensure that the following columns are numeric and not text: TIME, COBS, WT, AGE, AMT and DOSEs
 

b. Create a new column called BQLFLAG which takes a value of 
`0` if there is a numerical value in CObs and `1` if there is "BQL" in COBS.
    
c. Create a new column called "GENDER" where:
    i. Female = 0
    ii. Male = 1 
d. Create a new column called RACEN where:
    i. Caucasian = 0
    ii. Asian = 1
    iii. Black = 2
    iv. Hispanic = 3

f. Create a new column called "IDF" - unique subject ID as combination of formulation and ID 

g. Remove the following columns
    i. SEX
    ii. RACE

Save the above modifications as a new csv file

## Descriptive Statistics

1. show a summary for all demographic columns

```{r}
# single row per id
sid_pk_data <- pk_data_cobs %>%
  distinct(ID, .keep_all = TRUE) 

```

2. Count the number of subjects in each "Race" category

3. calculate the min, mean, and max values for WT, AGE:
    a. by Sex

* there are also targeted verbs in the form `<verb>_at` that can specify what
columns to act on, and which functions to run

4. What is the Average numbers samples(observations) per individual in this dataset. 
* Hint: make sure you are *only* counting samples, rows with AMT values are not considered observations.

5. Calculate the Mean, 5th, and 95th percentile concentration at each time point for each formulation and dose level. hint: you can use `?quantile` to calculate various quantiles


```{r}
devtools::session_info()
```

