# Diagnostic Plots

```{r}
library(PKPDmisc)
library(knitr)
library(tidyverse)
library(rlang)
```

* Create a Res vs Time function with loess fits for the central tendency and the spread (hint abs() is your friend for the spread). 
    * Conditionally allow the loess curve of central tendency to appear, 
    with a default of TRUE. 
    * Users should be able to specify the residual column name.
    * update your function to flag any point over some threshold as red, with a default of absolute difference of > 2.5 


1) read in the csv dataset:


```{r}
resid <- read_csv("../data/Residuals.csv")
```

* Residuals

1) Plot CWRES vs time after dose (TAD)

```{r}
resid %>%
  mutate(HIGHRES__ = factor(ifelse(abs(CWRES) > 2.5, 1, 0))) %>%
  ggplot(aes(x = TAD, y = CWRES)) +
  geom_point(aes(color = HIGHRES__)) +
  scale_color_manual(values = c("black", "red"), name = "outliers",
                     labels = c("not outlier", "outlier")) +
  geom_smooth(se= F) +
  geom_smooth(aes(y = abs(CWRES)), se = F) +
  geom_smooth(aes(y = -abs(CWRES)), se = F) +
  theme_bw()
```

```{r}
gg_res_time <- function(df, .time, .res, .threshold = 2.5, .ct = TRUE) {
  .time <- rlang::enexpr(.time)
  .res <- rlang::enexpr(.res)
  ggplot_output <- rlang::eval_tidy(
    rlang::quo(
    df %>%
    mutate(HIGHRES__ = factor(ifelse(abs(!!.res) > .threshold, 1, 0))) %>%
    ggplot(aes(x = !!.time, y = !!.res)) +
    geom_point(aes(color = HIGHRES__)) +
    scale_color_manual(values = c("black", "red"), name = "outliers",
                       labels = c("not outlier", "outlier")) +
    geom_smooth(aes(y = abs(!!.res)), se = F) +
    geom_smooth(aes(y = -abs(!!.res)), se = F) +
    theme_bw()
  ))
  if (!.ct) {
    return(ggplot_output)
  }
  
  return(ggplot_output +
    geom_smooth(se= F) 
    )
}

gg_res_time(resid, TAD, CWRES, 1.5, FALSE)
```

2) Plot WRES vs time after dose (TAD)

```{r}
gg_res_time(resid, TAD, WRES)
```

```{r}
devtools::session_info()
```

