# advanced ggplot customizations

Help! Your colleague Jon has come to you for help. He is just starting to use ggplot and is having trouble. Thankfully, he has gotten started on making the necessary plots, and has a good idea what he wants. Your job, should you choose to accept it, is to help finish off the plots Jon has started. 


Jon has been kind enough to provide you with a zipped R project. You can unzip the project and click on the .Rproj to open up the project to get you started. 

```{r libraries}
library(tidyverse, warn.conflicts = FALSE)
library(knitr)
library(PKPDdatasets)
library(PKPDmisc) 
opts_chunk$set(cache=T, fig.width=9)
```

The data Jon is working with conventiently comes from the `dapa_iv_oral` dataset in the `PKPDdatasets` package.

Jon's first attempt to make a concentration time plot for each ID looks funny. 

```{r echo=FALSE}
oral_data <- dapa_IV_oral %>% filter(FORMULATION == "ORAL")
```

```{r}
kable(head(oral_data))
```

```{r, fig.height = 6, fig.width = 10}
single_id <- oral_data %>%
  filter(ID == 1) 
mean_profile <- single_id %>% 
  group_by(TAD) %>%
  summarize(conc = mean(COBS)) %>% 
  mutate(TYPE = 1)

single_id %>%
ggplot( 
       aes(x = TAD, y = COBS,group = interaction(ID, OCC), color = factor(OCC))) + 
    geom_line(size = 1.1) + facet_wrap(~ID, scales="free_x") +
  labs(x = "Time After Dose, hrs", 
       y = "Concentration, ug/L", color = "Occasion", caption = "my caption", title = "my cool plot") +
  geom_line(data = mean_profile, 
            aes(y = conc, group = NULL, color = NULL, linetype = factor(TYPE)), size = 1.5) +
  scale_linetype_discrete(name = "mean timecourse")
```

```{r}
devtools::session_info()
```

