# Introduction to ggplot2

```{r}
library(PKPDmisc)
library(PKPDdatasets)
library(tidyverse)
```

## XY Plots
1) For concentration-time plots filter only OCC 1 from dapa_IV_oral (in PKPDdatasets) for subsequent plotting
```{r}
data1 <- dapa_IV_oral %>% filter(OCC == 1)
```

2) Basic Concentration-Time plot (point and lines)


3) make points/lines bigger


4) add log transformation to y axis


5) Add color by gender

BONUS: rename labels legend and move legend to top right

6) facet by race

Note, with facetting by race, the color becomes unnessary extra visual stimulus so we remove the color.

```{r}
data1 %>% 
    ggplot(aes(x = TIME, y = COBS, group = ID)) +
    geom_point(size = 2.5) + geom_line(size = 1.1) +
    scale_y_log10() +
    theme(legend.position = c(1, 1), legend.justification = c(1, 1)) +
    facet_wrap(~GENDER)
```

BONUS: rename facet strips by name

There are a couple ways of doing this:

  a) on the fly mutate the the values to labels
  
  b) Use facet_grid with the labeller argument


9) color by weight

BONUS: rename axes


## Boxplots and Histograms

* Histogram(s) of Weight with vertical line for median value

```{r}
# distinct is a dplyr verb - easiest way to subset data by the 
# first row in some combination.
sid_data <- data1 %>% 
    distinct(ID, .keep_all = TRUE) # single row per id data
```
  

```{r}
devtools::session_info()
```

