---
title: "data tidying hands-on"
author: "Devin"
date: "`r Sys.Date()`"
output:
  pdf_document: default
---

```{r}
library(knitr)
library(tidyverse, warn.conflicts = FALSE)
library(PKPDmisc)
```

## DATA IMPORT

```{r}
ebe_cov <- read_csv("../data/ebe_cov.csv")
```

Remove all the columns with ETAS and name dataframe `covs`

```{r}
covs <- ebe_cov %>% select(-contains("ETA"))
head(covs)
```

Find all columns with an NA value, and the associated ID

```{r}
missings <- covs %>% group_by(ID) %>%
  select_if(function(.x) {
  any(is.na(.x))
  }) %>% filter(is.na(BW) | is.na(SEX))
missings
```


Impute the NA values using the mean for any continous variable, and largest group for categorical

```{r}
mean_bw <- covs %>% select(ID, BW, SEX) %>%
  filter(!is.na(BW)) %>%
  summarize(meanBW = mean(BW))

counts <- covs %>% select(ID, BW, SEX) %>%
  filter(!is.na(SEX)) %>% count(SEX) %>% arrange(desc(n))
```

```{r}
covs_imputed <- covs %>% replace_na(list(
  BW = mean_bw$meanBW, 
  SEX = counts$SEX[[1]])) 
```


## data checkout for all covariates

Set all categorical covariates to factors with appropriate labels

```{r}
covs_imputed_fact <- covs_imputed %>%
  mutate(SEX = factor(SEX, 
                      levels = c(0, 1), 
                      labels = c("FEMALE", "MALE")),
         RACE = factor(RACE, levels = 0:2, labels = c("Asian", "Black", "Caucasian"))
)
```


Plot a scatter plot of all continuous covariates versus ID to check for visual outliers

```{r}
g_cont_covs <- covs_imputed_fact %>% 
  group_by(ID) %>% 
  select_if(is.numeric) %>%
  gather(contcov, cont_value, -ID) 

g_cont_covs %>%
  ggplot(aes(x = ID, y = cont_value)) + 
  geom_point() +
  facet_wrap(~contcov, scales = "free")
```


Plot a violin/box plot of all continuous covariates versus SEX to check for visual trends 

```{r}
covs_imputed_fact %>% gather(cont_covs, cont_values, BW:CRCL) %>%
  ggplot(aes(x = SEX, y = cont_values)) +
  geom_violin() + 
  facet_wrap(~cont_covs, scales = "free") +
  geom_jitter()
```


Plot a violin/box plot of all continuous covariates versus all categorical covariates to check for visual trends 

```{r}
devtools::session_info()
```

