---
title: "Probability of Target Attainment"
output: html_document
---

You have been tasked with providing a labeling recommendation for a new compound - `pageimab`.

A population PK model has been developed and written in mrgsolve based on pharmacokinetics 
explored in ascending dose studies looking at BID (every 12 hours) dosing ranging from 250-1500 mg, with 250, 500, and 1000 mg tablets available.


Consultation with your clinical collegues has identified that the ideal therapeutic range for the steady-state
trough values is between 8-25 mg/L. 

Likewise, to maintain adequate safety and efficacy profile for commercial
success, 85% of patients given a weight range of 40-140 kg must be within that window.

Use mrgsolve to develop a dosing recommendation.

```{r}
library(tidyverse)
library(PKPDmisc)
library(mrgsolve)
```

```{r}
pmod <- mread_cache("pageimab", "../models/")
```

```{r}
see(pmod)
```

## initial exploration
```{r}

all_sims <- map_df(c(250, 500, 1000, 1250), function(.amt) {
  ids <- data_frame(
  ID = 1:5000,
  time = 0,
  amt = .amt,
  ii = 12, 
  ss = 1, 
  evid =1, 
  cmt = 1
  ) %>% mutate(
  WT = runif(n(), 40, 140)
  )
  pmod %>% 
    #ev(amt = 500, ii = 12, ss = 1) %>%
    data_set(ids) %>%
    mrgsim() %>% as_data_frame %>%
    filter(time == 12) %>% 
    mutate(dose = .amt)
  })

```

```{r}
 ids <- data_frame(
  ID = 1:5000,
  time = 0,
  ii = 12, 
  ss = 1, 
  evid =1, 
  cmt = 1
  ) %>% mutate(
  WT = runif(n(), 40, 140),
  amt = ifelse(WT > 90, 1250, 750),
  dose = amt
  )
  all_sims <-  pmod %>% 
    #ev(amt = 500, ii = 12, ss = 1) %>%
    data_set(ids) %>%
    carry.out(dose) %>%
    mrgsim() %>% as_data_frame %>%
    filter(time == 12) 
```

```{r}
head(all_sims)
```

```{r}
all_sims %>% select(ID, dose, CP) %>%
  mutate(bin = set_bins(CP, c(8, 25))) %>%
  group_by(dose) %>%
  mutate(totalinds = n()) %>%
  group_by(dose, bin, totalinds) %>%
  count(dose, bin) %>%
  mutate(prop = n/totalinds)
```



