---
title: "Probability of Target Attainment"
output: html_document
---


You have been tasked with providing a labeling recommendation for a new compound - `pageimab`.

A population PK model has been developed and written in mrgsolve based on pharmacokinetics 
explored in ascending dose studies looking at BID (every 12 hours) dosing ranging from 250-1500 mg, with 250, 500, and 1000 mg tablets available.


Consultation with your clinical collegues has identified that the ideal therapeutic range for the steady-state
trough values is between 8-25 mg/L. 

Likewise, to maintain adequate safety and efficacy profile for commercial
success, 85% of patients given a weight range of 40-140 kg must be within that window.

Use mrgsolve to develop a dosing recommendation.

```{r}
library(tidyverse)
library(PKPDmisc)
library(mrgsolve)
```

```{r}
pmod <- mread_cache("pageimab", "../models/")
```

```{r}
pmod %>% see
```

```{r}
ids <- data_frame(
    ID = 1:1000,
    time = 0,
    cmt = 1,
    ss = 1,
    ii = 12,
    evid = 1
  ) %>%
  mutate(
    WT = round(runif(n(), 40, 140), 1)
  )
```

## Single dose attempt

```{r}
.x <- 250
results <- map_df(c(seq(250, 1500, 250)), function(.x) {
  ids_amt <- ids %>%
    mutate(amt = .x)
  sim_out <- pmod %>%
    data_set(ids_amt) %>%
    mrgsim() %>% as_data_frame
  
  props <- sim_out %>%
    filter(time == 12) %>%
  mutate(
    in_window = set_bins(CP, breaks = c(8, 25)),
    total = n()
    ) %>%
  group_by(in_window) %>%
  summarize(
    prop = round(n() / unique(total), 3),
    percent = prop * 100
  )
  return(props %>% mutate(dose = .x)) 
})

results %>% filter(in_window == 1)
```

After exploring single doses, no dose was able to successfully 

```{r}


ids_amt <- ids %>%
  mutate(
    amt = ifelse(WT > 90, 1250, 750)
  )

sim_out <- pmod %>%
data_set(ids_amt) %>%
mrgsim() %>% as_data_frame

props <- sim_out %>%
  filter(time == 12) %>%
  mutate(
    is_obese = ifelse(WT > 95, 1, 0),
    in_window = set_bins(CP, breaks = c(8, 25))
  ) %>%
  group_by(is_obese) %>%
  mutate(total = n()) %>%
  group_by(in_window, is_obese) %>%
  summarize(
    prop = round(n() / unique(total), 3),
    percent = prop * 100
  )

props %>% arrange(is_obese)

props %>%
  filter(in_window == 1)

props %>% arrange(is_obese)

```




